An Airdrop That Preserves Recipient Privacy

### 2019-01-18 paper/paper.tex
edits

%\def\useacmstyle{}
\def\submissionpapernumber{$\infty$}

\ifx\useacmstyle\undefined
    \documentclass[11pt]{article}
    \usepackage{fullpage}
    \usepackage[hidelinks]{hyperref}
\else
    \documentclass[sigconf,anonymous]{acmart}
    \fancyhf{}
    \fancyhead[C]{Anonymous submission \submissionpapernumber\ to ACM CCS 2019}
    \fancyfoot[C]{\thepage}
    \setcopyright{none}
    \acmConference{ACM CCS Submission}{2019 Feb 05}{}
    \acmYear{2019}
    \settopmatter{printacmref=false, printccs=false, printfolios=false}
\fi

\usepackage[dvipsnames]{xcolor}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
\usepackage{macros}
\usepackage[normalem]{ulem}
\usepackage{peanutgallery}

@@

\title{An Airdrop That Preserves Recipient Privacy}
\author{Dan Boneh \and Chris Jeffrey \and Joseph Poon \and Riad Wahby}

@@

To prove knowledge of the factorization of $n$ the prover
proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
That is, we provide a ZKPK for the relation
\begin{equation} \label{eq:lang}
  \mathcal{R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
        \text{s.t.}\ \ 
                \begin{aligned}
                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
                        2 & \leq t \leq \lambda  \ \textrm{a prime}
                \end{aligned}  \right\}.
\end{equation}
Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
The integer relation $w^2 = t + a\cdot n$ proves that 
$w^2 \equiv t \pmod{n}$, as required.
We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
residue modulo the committed $n$.  Leaking this bit of information about $n$
does not interfere with the application to a secure
\RSW{``secure'' $\rightarrow$ ``private''?}
airdrop.

@@

\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
parameterized by $g, h, c, c_1, c_2$ as follows:
\begin{equation} \label{eq:hom}
  \phi\left(\!\!\begin{array}{l}
                w, \mathit{w2}, \mathit{s1}, a, \\
                \mathit{na}, \mathit{s1w}, \mathit{sa}, \mathit{s2}
      \end{array}  \!\!\!\right) \deq
      \Bigl(\ 
       g^w \cdot h^{\mathit{s1}},\ \ \ 
       g^a \cdot h^{\mathit{s2}},\ \ \ 
       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
       \mathit{w2} - \mathit{na}\ \Bigr)
\end{equation}
It is easy to see that $\phi$ is a group homomorphism.
The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
We will write the group operation in this group multiplicatively.
That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
then 
\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]

@@

We design a ZKPK for a $\phi$-preimage 
using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
Here the verifier is given $T \in \GG^4 \times \ZZ$ 
and the prover is given $T$ and $\vv \in \ZZ^8$
where $\phi(\vv) = T$. 
The protocol works as follows:
\begin{enumerate}
\item The prover sets
    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$ where
\[ r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}} 
    \quad\text{and}\quad
   r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N}.
\]
The prover computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
and sends $(c_1, c_2, \Rv)$ to the verifier.

@@

\paragraph{Comment 1.}
The protocol is insecure if the group $\GG$ contains a non-identity
element of known order.  {\bf TODO: describe an attack.}
In the multiplicative group $(\ZZ/n)^*$ the
element $-1$ has order~$2$, and hence the protocol is insecure in this
group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
where elements are represented as integers in the interval $[1,n/2]$
and the product of $x$ and $y$ is defined as 
$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
In this group $-1$ is the same as $1$, and presumably there are
no other known elements of known order.

@@

\begin{theorem}
Protocol $\prot{P}$ is a zero-knowledge protocol
for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang}.
\end{theorem}

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\lnum \label{ln:randvell}
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randZ}
\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
\lnum \label{ln:sim}
\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover the quantities
$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
are chosen uniformly in $\range{N}$.
Consider one such value $r \rgets \range{N}$.
Because $N$ is much larger than $\abs{\GG} \cdot \ell$
we know that the pair
$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
Similarly,  in a real transcript
each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
each of these four values modulo $\ell$
is statistically close to uniform in $\range{\ell}$.
It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
Observe that each of the first four components of $\Zv_q$ is a group
element in $\GG$ that is randomized by
$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
 h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
 h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
 h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
independent of everything else in the transcript, it follows that
in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen 
on line~\eqref{ln:randZ} in the simulation.

It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
In a real transcript this $Z_5$ is computed as 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satisfies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the simulated $Z_5$ on line~\eqref{ln:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
However this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
The reason is that in both distributions, 
every possible value in the range of $Z_5$, 
except possibly at the edges, 
is obtained from the same number of values 
for the pair $(r_\text{w2}, r_\text{na})$. 
%%  would be good to prove this as a general lemma.
We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
is statistically close to its real distribution.

@@

\begin{definition}
We say that algorithm $\mathcal{G}$ is an \defn{honest instance
generator} for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}
if it chooses integers $n, s, t$, and outputs $(c, t)$ where
$c \deq g^n h^s \in \GG$. 
\end{definition}

\begin{theorem}
Protocol $\prot{P}$ is an argument of knowledge
for the relation $\mathcal{R}_{g,h}$ in \eqref{eq:lang} 
for instances $(c,t)$ generated by an honest instance
generator $\mathcal{G}$,
when the group $\GG$ is a modeled as a generic group of unknown order. 
\end{theorem}

\begin{proof}
We construct an extractor that given an instance $(c,t)$ 
generated by $\mathcal{G}$,
interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}. 
The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
The extractor rewinds the prover and obtains two
accepting transcripts
$\mathcal{T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
and 
$\mathcal{T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
Dividing the corresponding verification equations one by the other
we obtain
\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
          T^{\mathit{ch} - \mathit{ch}'}. \]
Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
Then plugging this into the definition of $\phi$ we obtain
\begin{equation} \label{eq:messy}
      (\Zv_q / \Zv_q')^\ell \cdot
      \left(\begin{array}{l}
       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
       \Delta \mathit{w2} - \Delta \mathit{na}\ 
       \end{array} \right)
          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
\end{equation}
Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
for $i=1,2,3,4$, 
and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
where the extractor knows all the listed integer exponents.
Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
to a generic group oracle query for a random group element.

@@

Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
For any pair of accepting transcripts such as $(\mathcal{T}_1, \mathcal{T}_2)$,
it must be the case that 
$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
Hence, by constructing a polynomial number of such accepting transcript pairs, 
the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.

@@

Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
repeating this procedure over several $\ell$ and then using the chinese
remainder theorem.  
Similarly, it can extract $s \in \ZZ$ from
the right equality in~\eqref{eq:third}.   
It thus obtains a witness $(n, s, w, a)$ 
for the relation $\mathcal{R}_{g,h}$ in~\eqref{eq:lang}, as required.
\end{proof}

>>>>

\documentclass[11pt]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
\usepackage{fullpage}
\usepackage{macros}
\usepackage[normalem]{ulem}
\usepackage{peanutgallery}

@@

\title{An Airdrop That Preserves Recipient Privacy}
\author{Dan Boneh \and Riad Wahby}

@@

To prove knowledge of the factorization of $n$ the prover
proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
That is, we provide a ZKPK for the relation
\begin{equation} \label{eq:lang}
  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
        \text{s.t.}\ \ 
                \begin{aligned}
                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
                        2 & \leq t \leq \lambda  \ \textrm{a prime}
                \end{aligned}  \right\}.
\end{equation}
Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
The integer relation $w^2 = t + a\cdot n$ proves that 
$w^2 \equiv t \pmod{n}$, as required.
We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
residue modulo the committed $n$.  Leaking this bit of information about $n$
does not interfere with the application to a secure
\RSW{``secure'' $\rightarrow$ ``private''?}
airdrop.

@@

\item Next, define a homomorphism $\phi:\ZZ^8 \to \GG^4 \times \ZZ$ 
parameterized by $g, h, c, c_1, c_2$ as follows:
\begin{equation} \label{eq:hom}
  \phi\left(\!\!\begin{array}{l}
                w, \mathit{w2}, s_1, a, \\
                \mathit{na}, \mathit{s1w}, \mathit{sa}, s_2
      \end{array}  \!\!\!\right) \deq
      \Bigl(\ 
       g^w \cdot h^{\mathit{s1}},\ \ \ 
       g^a \cdot h^{\mathit{s2}},\ \ \ 
       g^{\mathit{w2}} \cdot h^{\mathit{s1w}} / c_1^w,\ \ \ 
       g^{\mathit{na}} \cdot h^{\mathit{sa}} / c^a,\ \ \ 
       \mathit{w2} - \mathit{na}\ \Bigr)
\end{equation}
It is easy to see that $\phi$ is a group homomorphism.
The range of $\phi$ is the group $\GG^4 \times \ZZ$.  
We will write the group operation in this group multiplicatively.
That is, if $(a_i, b_i, c_i, d_i, e_i) \in \GG^4 \times \ZZ$ for $i=1,2$
then 
\[  (a_1, b_1, c_1, d_1, e_1) \cdot (a_2, b_2, c_2, d_2, e_2) \deq 
      (a_1 a_2,\ b_1 b_2,\ c_1 c_2,\ d_1 d_2,\ e_1 + e_2).  \]

@@

We design a ZKPK for a $\phi$-preimage 
using a zero-knowledge protocol from~\cite[\S 3.5]{ourpaper}.
Here the verifier is given $T \in \GG^4 \times \ZZ$ 
and the prover is given $T$ and $\vv \in \ZZ^8$
where $\phi(\vv) = T$. 
The protocol works as follows:
\begin{enumerate}
\item The prover chooses
 $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa} \rgets \range{{2^{2\lambda}}}$
 and
 $r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2} \rgets \range{N \cdot 2^{2^\lambda}}$ and sets
    $\rv \deq (r_w, r_\mathit{w2}, r_\mathit{s1}, r_a, r_\mathit{na}, 
                     r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}) \in \ZZ^8$. \\
It computes $\Rv \gets \phi(\rv) \in \GG^4 \times \ZZ$
and sends $(c_1, c_2, \Rv)$ to the verifier.

@@

\paragraph{Comment 1.}
The protocol is insecure if the group $\GG$ contains a non-identity
element of known order.  In the multiplicative group $(\ZZ/n)^*$ the
element $-1$ has order~$2$, and hence the protocol is insecure in this
group.  Instead, we can work in the quotient group $(\ZZ/n)/\{\pm 1\}$, 
where elements are represented as integers in the interval $[1,n/2]$
and the product of $x$ and $y$ is defined as 
$\abs{x \cdot y} = \min(z, n-z)$ where $z = (x \cdot y \bmod n)$.
In this group $-1$ is the same as $1$, and presumably there are
no other known elements of known order.

@@

\begin{theorem}
Protocol $\prot{P}$ is a zero-knowledge protocol
for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang}.
\end{theorem}

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $c_1, c_2 \rgets \GG,\ \ \ell \rgets \primes$, and
\ \ $\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\lnum \label{ln:randvell}
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\> choose random $Z_1, Z_2, Z_3, Z_4 \rgets \GG$, \\
\lnum \label{ln:sim}
\> choose random $\hat{r}_\text{w2}, \hat{r}_\text{na} \rgets \range{2^{2\lambda}}$
and set $Z_5 \deq \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor \hat{r}_\text{w2} / \ell \rfloor - \lfloor \hat{r}_\text{na} / \ell \rfloor \in \ZZ$, \\
\> set $\Zv_q \deq (Z_1, Z_2, Z_3, Z_4, Z_5)  \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
In a real transcript we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that the simulated $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover the quantities
$r_\mathit{s1}, r_\mathit{s1w}, r_\mathit{sa}, r_\mathit{s2}$
are chosen uniformly in $\range{N \cdot 2^{2^\lambda}}$.
Consider one such value $r \rgets \range{N \cdot 2^{2^\lambda}}$.
Because $N \cdot 2^{2\lambda}$ is much larger than $\abs{\GG} \cdot \ell$
we know that the pair
$\big(\lfloor r/\ell \rfloor \bmod \abs{\GG},\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{\,\abs{\GG}\,} \times \range{\ell}$.
Similarly,  in a real transcript
each of $r_w, r_\mathit{w2}, r_\mathit{na}, r_\mathit{sa}$
is chosen uniformly in $\range{2^{2 \lambda}}$ and therefore
each of these four values modulo $\ell$
is statistically close to uniform in $\range{\ell}$.
It follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in line~\eqref{ln:randvell} in the simulation.

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly.
Observe that each of the first four components of $\Zv_q$ is a group
element in $\GG$ that is randomized by
$h^{\lfloor r_\mathit{s1} / \ell \rfloor},\
 h^{\lfloor r_\mathit{s2} / \ell \rfloor},\
 h^{\lfloor r_\mathit{s1w} / \ell \rfloor},\
 h^{\lfloor r_\mathit{sa} / \ell \rfloor}$ respectively.
Because these four exponents are close to uniform in $\range{\,\abs{\GG}\,}$ and are
independent of everything else in the transcript, it follows that
in a real transcript $Z_1, Z_2, Z_3, Z_4$ are independent and close to uniform elements in $\GG$.  This is also how these elements are chosen in the simulation.

It remains to argue that $Z_5 \in \ZZ$ is simulated correctly. 
In a real transcript this $Z_5$ is computed as 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satisfies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1\}$. 
As argued above, in a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the simulated $Z_5$ in~\eqref{ln:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
However this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
The reason is that in both distributions, 
every possible value in the range of $Z_5$, 
except possibly at the edges, 
is obtained from the same number of values 
for the pair $(r_\text{w2}, r_\text{na})$. 
%%  would be good to prove this as a general lemma.
We thus conclude that the simulated $Z_5$ in~\eqref{ln:sim} 
is statistically close to its real distribution.

@@

\begin{definition}
We say that algorithm ${\cal G}$ is an \defn{honest instance
generator} for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}
if it chooses integers $n, s, t$, and outputs $(c, t)$ where
$c \deq g^n h^s \in \GG$. 
\end{definition}

\begin{theorem}
Protocol $\prot{P}$ is an argument of knowledge
for the relation ${\cal R}_{g,h}$ in \eqref{eq:lang} 
for instances $(c,t)$ generated by an honest instance
generator ${\cal G}$,
when the group $\GG$ is a modeled as a generic group of unknown order. 
\end{theorem}

\begin{proof}
We construct an extractor that given an instance $(c,t)$ 
generated by ${\cal G}$,
interacts with a convincing prover and outputs a witness $(n, s, w, a)$ 
for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}. 
The protocol transcript is $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
The extractor rewinds the prover and obtains two
accepting transcripts
${\cal T}_1 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$
and 
${\cal T}_2 \deq (c_1, c_2, \Rv, \ell, \mathit{ch}', \Zv_q', \zv_\ell')$.
Dividing the corresponding verification equations one by the other
we obtain
\[   (\Zv_q / \Zv_q')^\ell \cdot \phi(\zv_\ell - \zv_\ell') = 
          T^{\mathit{ch} - \mathit{ch}'}. \]
Let $\zv_\ell - \zv_\ell' = \Big(\Delta w,\ \Delta \mathit{w2},\ \Delta \mathit{s1},\ \Delta a,\ \Delta \mathit{na},\ \Delta \mathit{s1w},\ \Delta \mathit{sa},\ \Delta \mathit{s2} \Big) \in \ZZ^8$ and let $\Delta \mathit{ch} = \mathit{ch} - \mathit{ch}' \in \ZZ$.
Then plugging this into the definition of $\phi$ we obtain
\begin{equation} \label{eq:messy}
      (\Zv_q / \Zv_q')^\ell \cdot
      \left(\begin{array}{l}
       g^{\Delta w} \cdot h^{\Delta \mathit{s1}},\ \ \ 
       g^{\Delta a} \cdot h^{\Delta \mathit{s2}},\ \ \ 
       g^{\Delta \mathit{w2}} \cdot h^{\Delta \mathit{s1w}} / c_1^{\Delta w}, \\
       g^{\Delta \mathit{na}} \cdot h^{\Delta \mathit{sa}} / c^{\Delta a},\ \ \ 
       \Delta \mathit{w2} - \Delta \mathit{na}\ 
       \end{array} \right)
          = \left(\begin{array}{l}c_1, \ c_2, \ 1, \\ 1,\ t \end{array}\right)^{\Delta \mathit{ch}}.
\end{equation}
Let $\Zv_q / \Zv_q' = (z_1, z_2, z_3, z_4, z_5)$ 
where $z_1, z_2, z_3, z_4 \in \GG$ and $z_5 \in \ZZ$.  
In a generic group $\GG$, the group elements $z_1, z_2, z_3, z_4$ 
must satisfy $z_i = g^{\alpha_i} h^{\beta_i} c^{\gamma_i} \prod_{j=1}^q g_j^{\delta_{i,j}}$
for $i=1,2,3,4$, 
and $c_1 = g^{\alpha} h^{\beta} c^\gamma \prod_{j=1}^q g_j^{\delta_{j}}$,
and $c_2 = g^{\alpha_0} h^{\beta_0} c^\gamma \prod_{j=1}^q g_j^{\delta_{0,j}}$,
where the extractor knows all the listed integer exponents.
Here $g_1,\ldots,g_q \in \GG$ are random group elements produced in response
to a generic group oracle query for a random group element.

@@

Consider the left equalities in~\eqref{eq:first} and~\eqref{eq:firsta}.
Define $w \deq \alpha + n \cdot \gamma \in \ZZ$ 
and $a \deq \alpha_0 + n \cdot \gamma_0 \in \ZZ$.
For any pair of accepting transcripts such as $({\cal T}_1, {\cal T}_2)$,
it must be the case that 
$\Delta w \equiv w \cdot \Delta \mathit{ch} \pmod{\ell}$ and
$\Delta a \equiv a \cdot \Delta \mathit{ch} \pmod{\ell}$. 
The extractor knows $\Delta w,\ \Delta a$, and $\Delta \mathit{ch}$.
Hence, by constructing a polynomial number of such accepting transcript pairs, 
the extractor can recover $w, a \in \ZZ$ using the chinese remainder theorem.

@@

Because $a \neq 0$, the extractor can obtain $(n \bmod \ell)$
from the left equality in~\eqref{eq:third}, and thus extract $n \in \ZZ$ by
repeating this procedure over several $\ell$ and then using the chinese
remainder theorem.  
Similarly, it can extract $s \in \ZZ$ from
the right equality in~\eqref{eq:third}.   
It thus obtains a witness $(n, s, w, a)$ 
for the relation ${\cal R}_{g,h}$ in~\eqref{eq:lang}, as required.
\end{proof}
